Yoghurt under stress

### 2014-06-15 seminaire_Tanakalab.tex
use the enhanced version of the creep_experiment video, update Couette sketch

\tikzset{external/force remake}
\begin{frame}{Acid-set protein gel (Yoghurt)}
\begin{block}{Recipe}
\begin{itemize}
\item Water (\SI{30}{\celsius})
\item Sodium caseinate (milk protein) 4\%
\raisebox{0.6\normalbaselineskip}[0pt][0pt]{$\left.\rule{0pt}{1.1\normalbaselineskip}\right\}$ stable solution}
\item Glucono-$\delta$-lactone (GDL) 1\% $\Rightarrow$ slow acidification
\end{itemize}
\end{block}

@@

\section{Creep and yielding}

@@

%\tikzset{external/force remake}
\begin{frame}{The yoghurt creep experiment}
\movie[externalviewer]{\begin{tikzpicture}
\node[inner sep=0] (a) {\includegraphics[height=16\baselineskip]{creep_experiment.jpg}};
\begin{scope}[shift={(a.north west)}, shift={(7.2\baselineskip,-1.1\baselineskip)}, ultra thick]
	\draw[Accent1] ellipse[x radius=2.9\baselineskip, y radius=0.7\baselineskip] ++(2.9\baselineskip,0)  -- ++(0,-6.6\baselineskip)  ++(-2.9\baselineskip,0) ellipse[x radius=2.9\baselineskip, y radius=0.7\baselineskip] ++(-2.9\baselineskip,0)  -- ++(0,6.6\baselineskip);
	\shadedraw[Accent2,ball color=Accent2] ellipse[x radius=2\baselineskip, y radius=0.4\baselineskip] ++(2\baselineskip,0)  -- ++(0,-6.6\baselineskip)  ++(-2\baselineskip,0) ellipse[x radius=2\baselineskip, y radius=0.4\baselineskip] ++(-2\baselineskip,0)  -- ++(0,6.6\baselineskip);
	\fill[Accent2, left color=black,right color=black, middle color=Accent2, ] (-0.3\baselineskip,0) rectangle +(0.6\baselineskip, \baselineskip);
	\begin{scope}[Main]
		\node[draw, minimum height=3.5\baselineskip, minimum width=1.2\baselineskip] at (2.4\baselineskip,-3.35\baselineskip) (window){};
		\node[draw, minimum height=7.5\baselineskip, minimum width=4\baselineskip] at (7.5\baselineskip,-4\baselineskip) (USV){};
		\draw(window.north east) -- (USV.north west) (window.south east) -- (USV.south west);
		\node[right, text width=4\baselineskip] at (USV.east) {ultrasound region of interest};
	\end{scope}
\end{scope}
\draw[->] (window.north west) ++(-1em, 0.2em) -- +(1em,0) node[midway,above,inner sep=1pt] {$r$};
\draw[->] (window.north west) ++(-1em, 0.2em) -- +(0,-1em)  node[midway,left] {$z$};
\node[text width=4\baselineskip] at (-3\baselineskip,-2.5\baselineskip) {shear rate response};
\node at (5\baselineskip,-2.5\baselineskip) {strain response};
\end{tikzpicture}%
}{/home/mathieu/Dropbox/Yaourt/films/Yaourt141_enhanced.avi}
\end{frame}

>>>>

%\tikzset{external/force remake}
\begin{frame}{Acid-set protein gel (Yoghurt)}
\begin{block}{Recipe}
\begin{itemize}
\item Water (\SI{30}{\celsius})
\item Sodium caseinate (milk protein) 4\%
\raisebox{0.6\normalbaselineskip}[0pt][0pt]{$\left.\rule{0pt}{1.1\normalbaselineskip}\right\}$ stable solution}
\item Glucono-$\delta$-lactone (GDL) 1\% $\Rightarrow$ slow acidification
\end{itemize}
\end{block}

@@

\section*{Creep and yielding}

@@

\tikzset{external/force remake}
\begin{frame}{The yoghurt creep experiment}
\movie[externalviewer]{\begin{tikzpicture}
\node[inner sep=0] (a) {\includegraphics[height=16\baselineskip]{creep_experiment.jpg}};
\begin{scope}[shift={(a.north west)}, shift={(5.8\baselineskip,-1.1\baselineskip)}, ultra thick]
	\draw[Accent1, x radius=3.1\baselineskip, y radius=0.3\baselineskip] ellipse ++(3.1\baselineskip,0)  -- ++(0,-7.4\baselineskip)  ++(-3.1\baselineskip,0) ellipse[] ++(-3.1\baselineskip,0)  -- ++(0,7.4\baselineskip);
	\shadedraw[Accent2,ball color=Accent2, x radius=2\baselineskip, y radius=0.1\baselineskip] ellipse ++(2\baselineskip,0)  -- ++(0,-7.4\baselineskip)  ++(-2\baselineskip,0) ellipse[] ++(-2\baselineskip,0)  -- ++(0,7.4\baselineskip);
	\fill[Accent2, left color=black,right color=black, middle color=Accent2, ] (-0.3\baselineskip,0) rectangle +(0.6\baselineskip, \baselineskip);
	\begin{scope}[Main]
		\node[draw, minimum height=4.2\baselineskip, minimum width=1.5\baselineskip] at (2.5\baselineskip,-4\baselineskip) (window){};
		\node[draw, minimum height=7.2\baselineskip, minimum width=4\baselineskip] at (8.9\baselineskip,-4.2\baselineskip) (USV){};
		\draw(window.north east) -- (USV.north west) (window.south east) -- (USV.south west);
		\node[right, text width=4\baselineskip] at (USV.east) {ultrasound region of interest};
	\end{scope}
\end{scope}
\draw[->] (window.north west) ++(-1em, 0.2em) -- +(1em,0) node[midway,above,inner sep=1pt] {$r$};
\draw[->] (window.north west) ++(-1em, 0.2em) -- +(0,-1em)  node[midway,left] {$z$};
\draw[<->] ++(-2\baselineskip,-\baselineskip) -- +(-1.1\baselineskip,0) node[midway,above] {\SI{2}{\milli\metre}};
\node[text width=4\baselineskip] at (-3\baselineskip,-2.5\baselineskip) {shear rate response};
\node at (5\baselineskip,-2.5\baselineskip) {strain response};
\end{tikzpicture}%
}{/home/mathieu/Dropbox/Yaourt/films/Yaourt141_enhanced.avi}
\end{frame}
\tikzset{external/force remake=false}
